HPC--101\\Onboarding

### 2018-04-03 hpc_101/sections/04_cluster_interaction.tex
removed history, added lease option, fixed partition info

\subsection{Connecting to a cluster @ UH}
\begin{frame}
	\frametitle{Connecting to a cluster @ UH}
	\begin{description}[\setlength{\leftmargini}{0pt}]
	\item[] \begin{itemize}
		\item To connect to the cluster, an SSH client is required
		\item Linux and MacOS X, typically have a SSH client already installed
		\item Windows typically needs a 3rd party SSH client
		\item Suggested SSH clients for Windows include:
		\begin{itemize}
			\item \href{http://www.hawaii.edu/askus/685}{SSH Secure Shell}~(SSH 3.2.9)
			\item \href{http://www.chiark.greenend.org.uk/~sgtatham/putty/download.html}{Putty}
                        \item \href{http://mobaxterm.mobatek.net/}{MobaXterm}
		\end{itemize}
	\end{itemize}
	\item[] ~\\
	\item[] \begin{itemize}
		\item The {\craycs} has two login nodes:
		\begin{itemize}
			\item uhhpc1.its.hawaii.edu
			\item uhhpc2.its.hawaii.edu
		\end{itemize}
	\end{itemize}
	\end{description}
        ~\\~\\
	{\large Let's attempt to login!}
\end{frame}

\subsubsection{Login to the {\craycs}}
\begin{frame}
\frametitle{Login to the {\craycs}}
	\begin{center}\textbf{Windows}\end{center}
	\hrule~\\
	\begin{itemize}
		\item If SSH 3.2.9 installed (Lab PCs have it installed)
		\item Open the start menu, and type ``SSH'' and you should see a program called ``SSH Secure File Terminal Client''
		\item Click ``Quick Connect'' and enter the following information:
			\begin{itemize}
			\item[] \textbf{Host Name:} uhhpc1.its.hawaii.edu --OR-- uhhpc2.its.hawaii.edu
			\item[] \textbf{User Name:} Your UH User name e.g., user99
			\item[] \textbf{Port:} 22
			\end{itemize}
		\item Press ``Connect''
		\item Enter your UH user password when prompted and press the return key
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Login to the {\craycs}}
	\begin{center}\textbf{Mac \& Linux}\end{center}
	\hrule~\\
	\begin{itemize}
		\item Open a terminal window
		\item Enter one of the following:
		\begin{itemize}
			\item ssh $<$UH User name$>$@uhhpc1.its.hawaii.edu
			\item ssh $<$UH User name$>$@uhhpc2.its.hawaii.edu
			\item \textbf{Example:} ssh user99@uhhpc1.its.hawaii.edu
		\end{itemize}
		\item Enter your UH user password when prompted and press the return key
	\end{itemize}
\end{frame}

@@

\subsection{User Directories}
\begin{frame}[fragile]
\frametitle{User Directories}
\begin{block}{Home}
\begin{semiverbatim}\tiny \texttt
[user99@login \ctilde]\$ ls -l 
total 0
lrwxrwxrwx 1 user99 user99 23 Jan 15 20:38 \textcolor{teal}{apps} -> /lus/scratch/usr/user99
lrwxrwxrwx 1 user99 user99 19 Jan 15 20:38 \textcolor{teal}{lus} -> /lus/scratch/user99
lrwxrwxrwx 1 root   root   37 Jan 15 20:41 \colorbox{black}{\textcolor{red}{purge}} -> /lus/scratch/log/purge/current/user99
\end{semiverbatim}
\end{block}
	\begin{itemize}\footnotesize
		\item \ctilde{}/ is not on the {\lustre} filesystem and \textbf{should not be used for job data!}
		\item \ctilde{}/lus/ is a symlink to the {\lustre} scratch
		\begin{itemize}\tiny
			\item This is where all your job data files should live
			\item Items in this directory \emph{\textbf{are}} subject to our 90 day purge policy
		\end{itemize}
		\item \ctilde{}/apps/ is a symlink to where programs should be stored
		\begin{itemize}\tiny
			\item Items in this directory \emph{\textbf{are not}} subject to our 90 day purge policy
			\item Directory is monitored for abuse
		\end{itemize}
		\item \ctilde{}/purge/ is typically a dead symlink
		\begin{itemize}\tiny
			\item Symlink becomes active if the user has files that are part of the next automatic purge
			\item When \ctilde{}/purge/ is active, the directory containing two files -- \emph{purge\_list.txt} \& \emph{totals.txt}
			\item An email is sent to users if they have files that will be purged
			\item Email notification is sent out 14 days before the purge takes place
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{User Directories}
\begin{block}{Filesystems}
\begin{semiverbatim}\tiny \texttt
[user99@login \ctilde]\$ df -h
Filesystem                                  Size  Used Avail Use% Mounted on
10.10.0.3:/ha_cluster/home                  1.8T  888G  851G  52% /home
10.12.0.51@o2ib:10.12.0.52@o2ib:/scratch    582T  429T  125T  78% /lus/scratch
\end{semiverbatim}
\end{block}
	\begin{itemize}\footnotesize
		\item /home/$<$username$>$ exists on a NFS mounted filesystem
		\begin{itemize}\tiny
			\item Only has 1.8TB of useable space
			\item Using all this space may cause problems for the entire cluster
			\item Not a high performance filesystem and small in size
		\end{itemize}
		\item /lus/scratch/ is the {\lustre} filesystem
		\begin{itemize}\tiny
			\item Has 582TB of useable space
			\item \ctilde{}/apps/, \ctilde{}/lus/, and \ctilde{}/purge/ all point to directories on this filesystem
			\item High performance and a lot more space for users to use
			\item No hard or soft quotas are in place
			\item Utilization is managed through the 90 day purge policy
		\end{itemize}
	\end{itemize}
\end{frame}

@@

	\end{block}
	\begin{itemize}
		\item We globally install frequently requested software packages and create modules for all users to access
		\item Access to modules is via the \textbf{module} command
		\begin{itemize}\footnotesize
			\item `module avail' -- list installed modules
			\item `module show $<$module name$>$' -- Show what actions a module performs
			\item `module load $<$module name$>$' -- Loads the named module
			\item `module purge' -- Unload all loaded modules
		\end{itemize}
		\item Installing software in your \ctilde{}/apps directory is suggested to prevent us from being a bottleneck
	\end{itemize}

@@

\begin{frame}
\frametitle{Compilers}
	\begin{itemize}
		\item We have the {\intel} \& GNU (gcc, g$++$) compilers
		\item Compiling must take place on a compute node
		\begin{itemize}
			\item Interactive sessions are useful for compiling software
			\item Sandbox nodes mirror the environment the compute nodes provide and are ideal for compilation
			\item Login nodes \textbf{do not} load all the software and libraries found on the compute nodes
		\end{itemize}
		\item {\intel} compilers are recommended for best performance
		\begin{itemize}
			\item {\intel} 2013 compilers:
			\begin{itemize}
				\item module load intel/ics -- Loads {\intel} compilers: {\tiny \textbf{icc}, \textbf{ifort}, \textbf{icpc}}
				\item module load intel/impi -- Loads {\intel} MPI wrapper: {\tiny\textbf{mpiicc}, \textbf{mpiifort}, \textbf{mpiicpc}}
			\end{itemize}
			\item {\intel} 2016 compilers:
			\begin{itemize}
				\item We have 2 floating seats for {\intel} 2016 compiler
				\item intel\_2016/ics 
				\item intel\_2016/impi 
			\end{itemize}
		\end{itemize}			
	\end{itemize}
\end{frame}

@@

\subsection{SLURM Partitions}
\begin{frame}
\footnotesize
\frametitle{Partitions}
\begin{block}{What is a partition?}\footnotesize
A partition can be thought of as a group of nodes/resources divided into possibly overlapping sets.  Each partition can be considered as a job queue, each of which has an assortment of constraints such as job size limit, job time limit, users permitted to use it, etc. Priority-ordered jobs are allocated nodes within a partition until the resources (nodes, processors, memory, etc.) within that partition are exhausted.\footnote{\label{schedmd_qstart}\tiny \url{http://slurm.schedmd.com/quickstart.html}}
\end{block}
\begin{itemize}
	\item The {\craycs} currently has seven public partitions:~\\\textbf{community.q}, \textbf{exclusive.q}, \textbf{lm.q}, \textbf{gpu.q}, \textbf{sb.q}, \textbf{kill.q}, \textbf{htc.q}
	\item Jobs submitted to kill.q and htc.q can be preempted by jobs in other partitions
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Partition Details}
\resizebox{0.95\textwidth}{!}{%
\begin{tabular}{l || c || c || c || c || c || c}
\toprule                                                                    
\textbf{Partition} & \textbf{Time} & \textbf{Nodes per job} & \textbf{Priority} & \textbf{Shared} & \textbf{Preempt Mode} & \textbf{Memory per CPU (MB)} \\
%\toprule                                                                    
%\toprule                                                                    
\midrule
\midrule
community.q & \begin{tabular}{l r} \textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} & \begin{tabular}{c c} \textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} & \padfrom{\ \ \ }{20}\end{tabular} & 10 & NO & OFF & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}\end{tabular}\\
\hline
\hline
exclusive.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:}& \padfrom{\ \ \ }{1}~\\ \textbf{Max:}&\padfrom{\ \ \ }{20}\end{tabular} & 10 & EXCLUSIVE & OFF & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}\end{tabular}\\
\hline
\hline
gpu.q & \begin{tabular}{l r} \textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} & \begin{tabular}{c c} \textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} & \padfrom{\ \ \ }{1}\end{tabular} & 10 & NO & OFF & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}\end{tabular}\\
\hline
\hline
kill.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} &\padfrom{\ \ \ }{20}\end{tabular} & 10 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}\end{tabular}\\
\hline
\hline
htc.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} &\padfrom{\ \ \ }{1}\end{tabular} & 1 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}\end{tabular}\\
\hline
\hline
lm.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} &\padfrom{\ \ \ }{1}\end{tabular} & 10 & NO & OFF & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}\end{tabular}\\
\hline
\hline
sb.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:05:00~\\ \textbf{Max:} & 0-01:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} &\padfrom{\ \ \ }{2}\end{tabular} & 10 & NO & OFF & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}\end{tabular}\\
\bottomrule 
\end{tabular}   
}
\\
\bigskip
Partition details also available on the \href{http://www.hawaii.edu/its/ci/hpc-resources/slurm-partitions/}{{\ci} website} or by using the following command:
\\
\texttt{$[$login \ctilde$]$\$ scontrol show partition $<$partition name$>$}
\end{frame}

>>>>

\subsection{Connecting to a cluster @ UH}
\begin{frame}
	\frametitle{Connecting to a cluster @ UH}
	\begin{description}[\setlength{\leftmargini}{0pt}]
	\item[] \begin{itemize}
		\item To connect to the cluster, an SSH client is required
		\item Linux and MacOS X, typically have a SSH client already installed
		\item Windows typically needs a 3rd party SSH client
		\item Suggested SSH clients for Windows include:
		\begin{itemize}
			\item \href{http://www.hawaii.edu/askus/685}{SSH Secure Shell}~(SSH 3.2.9)
			\item \href{http://www.chiark.greenend.org.uk/~sgtatham/putty/download.html}{Putty}
                        \item \href{http://mobaxterm.mobatek.net/}{MobaXterm}
		\end{itemize}
	\end{itemize}
	\item[] ~\\
	\item[] \begin{itemize}
		\item The {\craycs} has one active login node:
		\begin{itemize}
			\item uhhpc1.its.hawaii.edu
			%\item uhhpc2.its.hawaii.edu
		\end{itemize}
	\end{itemize}
	\end{description}
        ~\\~\\
	{\large Let's attempt to login!}
\end{frame}

\subsubsection{Login to the {\craycs}}
\begin{frame}
\frametitle{Login to the {\craycs}}
	\begin{center}\textbf{Windows}\end{center}
	\hrule~\\
	\begin{itemize}
		\item If SSH 3.2.9 installed (Lab PCs have it installed)
		\item Open the start menu, and type ``SSH'' and you should see a program called ``SSH Secure File Terminal Client''
		\item Click ``Quick Connect'' and enter the following information:
			\begin{itemize}
			\item[] \textbf{Host Name:} uhhpc1.its.hawaii.edu %--OR-- uhhpc2.its.hawaii.edu
			\item[] \textbf{User Name:} Your UH User name e.g., user99
			\item[] \textbf{Port:} 22
			\end{itemize}
		\item Press ``Connect''
		\item Enter your UH user password when prompted and press the return key
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Login to the {\craycs}}
	\begin{center}\textbf{Mac \& Linux}\end{center}
	\hrule~\\
	\begin{itemize}
		\item Open a terminal window
		\item Enter one of the following:
		\begin{itemize}
			\item ssh $<$UH User name$>$@uhhpc1.its.hawaii.edu
%			\item ssh $<$UH User name$>$@uhhpc2.its.hawaii.edu
			\item \textbf{Example:} ssh user99@uhhpc1.its.hawaii.edu
		\end{itemize}
		\item Enter your UH user password when prompted and press the return key
	\end{itemize}
\end{frame}

@@

\subsection{User Directories}
\begin{frame}[fragile]
\frametitle{User Directories}
\begin{block}{Home}
\begin{semiverbatim}\tiny \texttt
[user99@login \ctilde]\$ ls -l 
total 0
lrwxrwxrwx 1 user99 user99 23 Jan 15 20:38 \textcolor{teal}{apps} -> /lus/scratch/usr/user99
lrwxrwxrwx 1 user99 user99 19 Jan 15 20:38 \textcolor{teal}{lus} -> /lus/scratch/user99

\end{semiverbatim}
\end{block}
% lrwxrwxrwx 1 root   root   37 Jan 15 20:41 \colorbox{black}{\textcolor{red}{purge}} -> /lus/scratch/log/purge/current/user99
\begin{itemize}\footnotesize
		\item \ctilde{}/ is not on the {\lustre} filesystem and \textbf{should not be used for job data!}
		\item \ctilde{}/lus/ is a symlink to the {\lustre} scratch
		\begin{itemize}\tiny
			\item This is where all your job data files should live
			\item Items in this directory \emph{\textbf{are}} subject to our purge policy
		\end{itemize}
		\item \ctilde{}/apps/ is a symlink to where programs should be stored
		\begin{itemize}\tiny
			\item Items in this directory \emph{\textbf{are not}} subject to our purge policy
			\item Directory is monitored for abuse
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{User Directories}
\begin{block}{Filesystems}
\begin{semiverbatim}\tiny \texttt
[user99@login \ctilde]\$ df -h
Filesystem                                  Size  Used Avail Use% Mounted on
10.10.0.3:/ha_cluster/home                  1.8T  888G  851G  52% /home
10.12.0.51@o2ib:10.12.0.52@o2ib:/scratch    582T  429T  125T  78% /lus/scratch
\end{semiverbatim}
\end{block}
	\begin{itemize}\footnotesize
		\item /home/$<$username$>$ exists on a NFS mounted filesystem
		\begin{itemize}\tiny
			\item Only has 1.8TB of useable space
			\item Using all this space may cause problems for the entire cluster
			\item Not a high performance filesystem and small in size
		\end{itemize}
		\item /lus/scratch/ is the {\lustre} filesystem
		\begin{itemize}\tiny
			\item Has 582TB of useable space
			\item \ctilde{}/apps/, \ctilde{}/lus/, and \ctilde{}/purge/ all point to directories on this filesystem
			\item High performance and a lot more space for users to use
			\item No hard or soft quotas are in place
			\item Utilization is managed through the  purge policy
		\end{itemize}
	\end{itemize}
\end{frame}

@@

	\end{block}
	\begin{itemize}
		\item We globally install frequently requested software packages and create modules for all users to access
		\item Access to modules is via the \textbf{module} command
		\begin{itemize}\footnotesize
			\item `module avail' -- list installed modules
			\item `module show $<$module name$>$' -- Show what actions a module performs
			\item `module load $<$module name$>$' -- Loads the named module
                        \item `module list -- Show what modules are loaded
			\item `module purge' -- Unload all loaded modules
		\end{itemize}
		\item Installing software in your \ctilde{}/apps directory is suggested to prevent us from being a bottleneck
	\end{itemize}

@@

\begin{frame}
\frametitle{Compilers}
	\begin{itemize}
		\item We have the {\intel} \& GNU (gcc, g$++$) compilers
		\item Compiling must take place on a compute node
		\begin{itemize}
			\item Interactive sessions are useful for compiling software
			\item Sandbox nodes mirror the environment the compute nodes provide and are ideal for compilation
			\item Login nodes \textbf{do not} mirror the compute node environment
		\end{itemize}
		\item {\intel} compilers are recommended for best performance
		\begin{itemize}
			\item {\intel} 2013 compilers:
			\begin{itemize}
				\item module load intel/ics -- Loads {\intel} compilers: {\tiny \textbf{icc}, \textbf{ifort}, \textbf{icpc}}
				\item module load intel/impi -- Loads {\intel} MPI wrapper: {\tiny\textbf{mpiicc}, \textbf{mpiifort}, \textbf{mpiicpc}}
			\end{itemize}
			\item {\intel} 2016 compilers:
			\begin{itemize}
				\item We have 2 floating seats for {\intel} 2016 compiler
				\item intel\_2016/ics 
				\item intel\_2016/impi 
			\end{itemize}
		\end{itemize}			
	\end{itemize}
\end{frame}

@@

\subsection{SLURM Partitions}
\begin{frame}
\footnotesize
\frametitle{Partitions}
\begin{block}{What is a partition?}\footnotesize
A partition can be thought of as a group of nodes/resources divided into possibly overlapping sets.  Each partition can be considered as a job queue, each of which has an assortment of constraints such as job size limit, job time limit, users permitted to use it, etc. Priority-ordered jobs are allocated nodes within a partition until the resources (nodes, processors, memory, etc.) within that partition are exhausted.\footnote{\label{schedmd_qstart}\tiny \url{http://slurm.schedmd.com/quickstart.html}}
\end{block}
\begin{itemize}
	\item The current public partitions on the {\craycs}:~\\\textbf{community.q}, \textbf{exclusive.q}, \textbf{lm.q}, \textbf{gpu.q}, \textbf{sb.q}, \textbf{kill.q}, \textbf{kill.gpu.q}, \textbf{htc.q}
	\item Jobs submitted to kill.q and htc.q can be preempted by jobs in other partitions
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Partition Details}
\resizebox{0.95\textwidth}{!}{%
\begin{tabular}{l || c || c || c || c || c || c}
\toprule                                                                    
\textbf{Partition} & \textbf{Time} & \textbf{Nodes per job} & \textbf{Priority} & \textbf{Shared} & \textbf{Preempt Mode} & \textbf{Memory per CPU (MB)} \\
%\toprule                                                                    
%\toprule                                                                    
\midrule
\midrule
community.q & \begin{tabular}{l r} \textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} & \begin{tabular}{c c} \textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} & \padfrom{\ \ \ }{1}\end{tabular} & 10 & NO & OFF & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}\end{tabular}\\
\hline
\hline
exclusive.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:}& \padfrom{\ \ \ }{1}~\\ \textbf{Max:}&\padfrom{\ \ \ }{20}\end{tabular} & 10 & EXCLUSIVE & OFF & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}\end{tabular}\\
\hline
\hline
gpu.q & \begin{tabular}{l r} \textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} & \begin{tabular}{c c} \textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} & \padfrom{\ \ \ }{1}\end{tabular} & 10 & NO & OFF & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}\end{tabular}\\
\hline
\hline
kill.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} &\padfrom{\ \ \ }{20}\end{tabular} & 10 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}\end{tabular}\\
\hline
\hline
kill.gpu.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} &\padfrom{\ \ \ }{1}\end{tabular} & 10 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}\end{tabular}\\
\hline
\hline
htc.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} &\padfrom{\ \ \ }{1}\end{tabular} & 1 & NO & REQUEUE & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}\end{tabular}\\
\hline
\hline
lm.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:10:00~\\ \textbf{Max:} & 3-00:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} &\padfrom{\ \ \ }{1}\end{tabular} & 10 & NO & OFF & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}\end{tabular}\\
\hline
\hline
sb.q & \begin{tabular}{l r}\textbf{Default:} & 0-00:05:00~\\ \textbf{Max:} & 0-01:00:00\end{tabular} &  \begin{tabular}{c  c}\textbf{Min:} & \padfrom{\ \ \ }{1}~\\ \textbf{Max:} &\padfrom{\ \ \ }{2}\end{tabular} & 10 & NO & OFF & \begin{tabular}{l c}\textbf{Default:} & \padfrom{\ \ \ \ \ \ \ }{3250}~\\ \textbf{Max:} & \padfrom{\ \ \ \ \ \ \ \ }{$\infty$}\end{tabular}\\
\bottomrule 
\end{tabular}   
}
\\
\bigskip
Partition details also available on the \href{http://www.hawaii.edu/its/ci/hpc-resources/slurm-partitions/}{{\ci} website} or by using the following command:
\\
\texttt{$[$login \ctilde$]$\$ scontrol show partition $<$partition name$>$}
\end{frame}

### 2018-04-03 hpc_101/sections/07_policies.tex
removed history, added lease option, fixed partition info

@@

\subsection{Lustre Filesystem Purge Policies}
\begin{frame}
\frametitle{{\lustre} Filesystem Purge Policies}
Due to users not having any quotas on the {\lustre} filesystem, we need some policy in place which removes older files from the system.  To accomplish this, we have currently implemented a purge policy, for any file that is older than 90 days.
\begin{itemize}
 \item Which of my directories are subject to the purge policy?
   \begin{itemize}
   \item \textbf{Answer:} All files and folders found in \ctilde/lus/ are subject to the 90 day purge policy.  Symlinks are excluded from the purge, and are not followed by the purge bot.  
   \end{itemize}
\item How frequently are files for purging identified?
   \begin{itemize}
   \item \textbf{Answer:} Taking into account the fill rate of the {\lustre} filesystem, a purge is performend as usage approaches 80\%.
   \end{itemize}
\end{itemize}
\btVFill
\begin{center}
\footnotesize \textbf{\emph{Purge policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
\end{center}
\end{frame}

>>>>

\subsection{Use and Management of IT Resources @ UH }
\begin{frame}
  \frametitle{Use and Management of IT Resources @ UH }
  All usage of the {\craycs} must be in compliance with \href{http://www.hawaii.edu/infotech/policies/itpolicy.html\#appendixa}{Chapter 708, Hawaii Revised Statutes} and is subject to University of Hawaii Executive Policy \href{http://www.hawaii.edu/infotech/policies/itpolicy.html}{E2.210}. 
\end{frame}

@@

\subsection{Lustre Filesystem Purge Policies}
\begin{frame}
\frametitle{{\lustre} Filesystem Purge Policies}
Due to users not having any quotas on the {\lustre} filesystem, we need some policy in place which removes older files from the system.  To accomplish this, we have currently implemented a purge policy, for any file that is older than 30 days.
\begin{itemize}
 \item What in \ctilde/lus/ is subject to the purge policy?
   \begin{itemize}
   \item \textbf{Answer:} Everything but directories and files between 1 byte and 32 Kilobytes are subject to the purge policy.
   \end{itemize}
%\item How frequently are files for purged?
%   \begin{itemize}
%   \item \textbf{Answer:} Taking into account the fill rate of the {\lustre} filesystem, a purge is performend as usage approaches 80\%.
%   \end{itemize}
\end{itemize}
\btVFill
\begin{center}
\footnotesize \textbf{\emph{Purge policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
\end{center}
\end{frame}
